Reasoning about a Capability Machine with Local Capabilities\\ Provably Safe Stack and Return Pointer Management (without OS Support)

### 2017-02-15 csf-2017/paper.tex
Slight tuning of the abstract.

\begin{abstract}  
  Capability machines provide security guarantees at machine level which makes
  them an interesting target for compilation schemes that aim to provably
  enforce properties like control-flow correctness, encapsulation of local
  state. We provide a formalization of a representative capability machine and
  propose a novel calling convention for enforcing control-flow correctness and
  encapsulation of local state on it. To prove these properties, we provide a
  logical relation that semantically captures the guarantees provided by the
  hardware (a form of capability safety). These results are not tied to our
  calling convention and can be used to reason about arbitrary programs.
\end{abstract}

>>>>

\begin{abstract}  
  Capability machines provide security guarantees at machine level which makes
  them an interesting target for compilation schemes that provably enforce
  properties like control-flow correctness, encapsulation of local state. We
  provide a formalization of a representative capability machine with local
  capabilities and propose a novel calling convention for enforcing control-flow
  correctness and encapsulation of local state on it. To prove these properties,
  we provide a logical relation that semantically captures the guarantees
  provided by the hardware (a form of capability safety). These results are not
  tied to our calling convention and can be used to reason about arbitrary
  programs.
\end{abstract}
